\section{Chapter 3: Bootstrap & RWD}

This document covers the principles of creating websites that look good on all devices and introduces the Bootstrap 5 framework for faster development.

\begin{tcolorbox}[colback=red!5,colframe=red!75,title=Exam Tips \& Hints]
\begin{itemize}
    \item \textbf{Viewport}: The \texttt{<meta name="viewport" ...>} tag is the single most common question about RWD setup.
    \item \textbf{Grid Sizing}: Understand the difference between \texttt{.container} (fixed widths at breakpoints) and \texttt{.container-fluid} (100\% width always).
    \item \textbf{Breakpoints}: Memorize the standard Bootstrap breakpoints (sm, md, lg, xl, xxl).
    \item \textbf{12 Columns}: Every row in Bootstrap is divided into 12 columns. Ensure your \texttt{col-*} classes in a single row add up to 12 for standard layout.
\end{itemize}
\end{tcolorbox}

\subsection{Responsive Web Design (RWD) Fundamentals}
Responsive Web Design is about creating websites that automatically adjust to different screen sizes, from mobile phones to large desktops.

\subsubsection{The Viewport Meta Tag}
To ensure proper rendering on mobile devices, always include the viewport meta tag in the \texttt{<head>}:
\begin{lstlisting}[language=HTML]
<meta name="viewport" content="width=device-width, initial-scale=1.0">
\end{lstlisting}

\subsubsection{Box-Sizing}
Standard box model adds padding and borders to the width, which can break layouts. Use \texttt{box-sizing: border-box} to include them within the defined width:
\begin{lstlisting}[language=CSS]
* {
  box-sizing: border-box;
}
\end{lstlisting}

\subsubsection{Responsive Images}
Make images scale automatically to fit their container:
\begin{lstlisting}[language=CSS]
img {
  max-width: 100%;
  height: auto;
}
\end{lstlisting}

\subsection{Layout Techniques}
\subsubsection{Grid System (12 Columns)}
Modern responsive design often uses a 12-column grid. The page is divided into 12 equal parts, and elements are assigned a number of columns.
\begin{itemize}
    \item \textbf{Float-based}: Older method using \texttt{float: left} and percentage widths.
    \item \textbf{Flexbox}: Modern method using \texttt{display: flex}.
    \item \textbf{CSS Grid}: Powerful layout engine using \texttt{display: grid}.
\end{itemize}

\subsubsection{Media Queries (\texttt{@media})}
Allows applying CSS rules based on device characteristics (like width).
\begin{lstlisting}[language=CSS]
/* Styling for mobile (Mobile First) */
.column { width: 100%; }

/* Styling for desktop (larger than 768px) */
@media screen and (min-width: 768px) {
  .column { width: 50%; }
}
\end{lstlisting}

\begin{tcolorbox}[colback=teal!5,colframe=teal!75,title=Practical Example: Mobile First Design]
Standard workflow starting from mobile and scaling up:
\begin{lstlisting}[language=CSS]
/* Default (Mobile) */
.content {
  padding: 10px;
  font-size: 14px;
}

/* Tablets (min 600px) */
@media screen and (min-width: 600px) {
  .content { padding: 20px; }
}

/* Desktop (min 1024px) */
@media screen and (min-width: 1024px) {
  .content { font-size: 18px; }
}
\end{lstlisting}
\end{tcolorbox}

\subsection{Introduction to Bootstrap 5}
Bootstrap is a free front-end framework for faster and easier web development. It includes design templates for typography, forms, buttons, tables, and many UI components.

\subsubsection{Getting Started}
Include Bootstrap via CDN in your \texttt{<head>}:
\begin{lstlisting}[language=HTML]
<link href="https://cdn.jsdelivr.net/npm/bootstrap@5.3.3/dist/css/bootstrap.min.css" rel="stylesheet">
<script src="https://cdn.jsdelivr.net/npm/bootstrap@5.3.3/dist/js/bootstrap.bundle.min.js"></script>
\end{lstlisting}

\subsubsection{The Grid System}
Built with flexbox and allows up to 12 columns.
\begin{itemize}
    \item \textbf{Structure}: \texttt{.container} $>$ \texttt{.row} $>$ \texttt{.col-*}
    \item \textbf{Classes for breakpoints}:
    \begin{itemize}
        \item \texttt{.col-}: Extra small ($<$576px)
        \item \texttt{.col-sm-}: Small ($\ge$576px)
        \item \texttt{.col-md-}: Medium ($\ge$768px)
        \item \texttt{.col-lg-}: Large ($\ge$992px)
        \item \texttt{.col-xl-}: Extra Large ($\ge$1200px)
        \item \texttt{.col-xxl-}: Extra Extra Large ($\ge$1400px)
    \end{itemize}
\end{itemize}

\begin{tcolorbox}[colback=cyan!5,colframe=cyan!75,title=Practical Example: Bootstrap 12-Column Grid]
A responsive row that changes layout based on screen size:
\begin{lstlisting}[language=HTML]
<div class="container">
  <div class="row">
    <!-- Full width on mobile, half on medium, third on large -->
    <div class="col-12 col-md-6 col-lg-4">Column 1</div>
    <div class="col-12 col-md-6 col-lg-4">Column 2</div>
    <div class="col-12 col-md-12 col-lg-4">Column 3</div>
  </div>
</div>
\end{lstlisting}
\end{tcolorbox}

\subsection{Bootstrap Components}
Boostrap provides a wide range of pre-styled components:
\begin{itemize}
    \item \textbf{Alerts}: Contextual feedback (e.g., \texttt{.alert-success}, \texttt{.alert-danger}).
    \item \textbf{Badges}: Labels and counts within other elements.
    \item \textbf{Buttons}: Custom styles for actions (e.g., \texttt{.btn}, \texttt{.btn-primary}, \texttt{.btn-outline-secondary}).
    \item \textbf{Cards}: Flexible content containers with headers, footers, and images.
    \item \textbf{Carousel}: A slideshow for cycling through images or text.
    \item \textbf{Navbar}: Responsive navigation headers.
    \item \textbf{Pagination}: Large hit areas for multi-page navigation.
    \item \textbf{Progress Bars}: Indicate work progress with labels.
    \item \textbf{Spinners \& Toasts}: Loading indicators and push-notifications.
\end{itemize}

\begin{tcolorbox}[colback=indigo!5,colframe=indigo!75,title=Practical Example: Bootstrap Components]
Using a Navbar and a simple Alert:
\begin{lstlisting}[language=HTML]
<!-- Responsive Navbar -->
<nav class="navbar navbar-expand-lg navbar-dark bg-dark">
  <div class="container">
    <a class="navbar-brand" href="#">Logo</a>
    <button class="navbar-toggler" data-bs-toggle="collapse" data-bs-target="#myNav">
      <span class="navbar-toggler-icon"></span>
    </button>
    <div class="collapse navbar-collapse" id="myNav">
      <ul class="navbar-nav">
        <li class="nav-item"><a class="nav-link" href="#">Home</a></li>
      </ul>
    </div>
  </div>
</nav>

<!-- Success Alert -->
<div class="alert alert-success mt-3">
  Registration Successful!
</div>
\end{lstlisting}
\end{tcolorbox}
\input{qa_fragments/ch3_qa}



