\section{Chapter 9: Redux - State Management}

Redux is a predictable state container for JavaScript apps. It helps you write applications that behave consistently, run in different environments (client, server, and native), and are easy to test.

\begin{tcolorbox}[colback=red!5,colframe=red!75,title=Exam Tips \& Hints]
\begin{itemize}
    \item \textbf{Principles}: Single source of truth (Store), State is read-only (Actions), Changes are made with pure functions (Reducers).
    \item \textbf{Data Flow}: Unidirectional data flow: Action $\rightarrow$ Reducer $\rightarrow$ Store $\rightarrow$ View.
    \item \textbf{Hooks}: Familiarize yourself with \texttt{useSelector} and \texttt{useDispatch} for modern Redux.
    \item \textbf{Immutability}: Never mutate the state directly in a reducer; always return a new object/array.
\end{itemize}
\end{tcolorbox}

\subsection{Core Concepts}
\begin{enumerate}
    \item \textbf{Store}: The centralized place where the state of the application is stored.
    \item \textbf{Actions}: Plain JavaScript objects that describe "what happened". Every action must have a \texttt{type} property.
    \item \textbf{Reducers}: Pure functions that specify how the application's state changes in response to an action.
    \item \textbf{Dispatch}: The method used to send actions to the store.
    \item \textbf{Connect}: A function (mostly used in class components) from \texttt{react-redux} to link React components to the Redux store.
\end{enumerate}

\begin{tcolorbox}[colback=blue!5,colframe=blue!75,title=Practical Example: Basic Redux Setup]
A simple counter example:
\begin{lstlisting}[language=JavaScript]
// 1. Action Types
const INCREMENT = 'INCREMENT';

// 2. Action Creator
const incrementAction = () => ({ type: INCREMENT });

// 3. Reducer
const counterReducer = (state = { count: 0 }, action) => {
  switch (action.type) {
    case INCREMENT:
      return { ...state, count: state.count + 1 };
    default:
      return state;
  }
};

// 4. Store
import { createStore } from 'redux';
const store = createStore(counterReducer);

// 5. Usage
store.dispatch(incrementAction());
console.log(store.getState()); // { count: 1 }
\end{lstlisting}
\end{tcolorbox}

\input{qa_fragments/ch9_qa}

