\subsection*{Comprehensive Exam Prep: HTML}

\begin{tcolorbox}[colback=blue!5,colframe=blue!75,title=Past Paper Questions (Sessional \& Final)]
\begin{enumerate}
    \item \textbf{MCQ:} Which HTML attribute is used to define inline styles? \textit{(Sessional 1 2025)}
    \begin{enumerate}[label=\alph*.]
        \item style
        \item class
        \item styles
        \item font
    \end{enumerate}
    \textbf{Answer:} a) style

    \item \textbf{MCQ:} What is the correct HTML element for the largest heading? \textit{(Final 2024)}
    \begin{enumerate}[label=\alph*.]
        \item \texttt{<h1>}
        \item \texttt{<h6>}
        \item \texttt{<head>}
        \item \texttt{<header>}
    \end{enumerate}
    \textbf{Answer:} a) \texttt{<h1>}

    \item \textbf{MCQ:} Which HTML attribute is used to provide a unique identifier for an element?
    \textbf{Answer:} a) id

    \item \textbf{MCQ:} What does the \texttt{<ol>} tag represent in HTML?
    \textbf{Answer:} a) Ordered List

    \item \textbf{Fill in the blank:} To make a hyperlink open in a new browser tab, the attribute of the \texttt{<a>} tag is \textbf{target} and should be set to \textbf{\_blank}.
\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colback=gray!5,colframe=gray!75,title=Extra Practice Questions]
\subsubsection*{Multiple Choice Questions}
\begin{enumerate}[resume]
    \item Which tag is used to create a drop-down list?
    \begin{enumerate}[label=\alph*.]
        \item \texttt{<input type="dropdown">}
        \item \texttt{<list>}
        \item \texttt{<select>}
        \item \texttt{<option>}
    \end{enumerate}
    \textbf{Answer:} c) \texttt{<select>}

    \item Which semantic tag determines the footer of a document or section?
    \begin{enumerate}[label=\alph*.]
        \item \texttt{<bottom>}
        \item \texttt{<footer>}
        \item \texttt{<section>}
        \item \texttt{<aside>}
    \end{enumerate}
    \textbf{Answer:} b) \texttt{<footer>}
\end{enumerate}

\subsubsection*{Code Analysis}
\textbf{Question:} Write the HTML code to create a form that sends data to \texttt{/submit} using the \texttt{POST} method. It should contain a text field for "Name" and a submit button.
\begin{lstlisting}[language=HTML]
<form action="/submit" method="POST">
    <label for="name">Name:</label>
    <input type="text" id="name" name="user_name">
    <button type="submit">Submit</button>
</form>
\end{lstlisting}

\subsubsection*{Theory Short Questions}
\begin{itemize}
    \item \textbf{Difference between Block and Inline elements:}
    \begin{itemize}
        \item \textbf{Block}: Starts on a new line and takes up full width (e.g., \texttt{div}, \texttt{p}, \texttt{h1}).
        \item \textbf{Inline}: Starts on the same line and takes only necessary width (e.g., \texttt{span}, \texttt{a}, \texttt{img}).
    \end{itemize}
    \item \textbf{Purpose of the \texttt{alt} attribute:} 
    \newline Provides alternative text for screen readers (accessibility) and displays if the image fails to load.
\end{itemize}
\end{tcolorbox}
