\subsection*{Comprehensive Exam Prep: JavaScript}

\begin{tcolorbox}[colback=yellow!5,colframe=yellow!75,title=Past Paper Questions]
\begin{enumerate}
    \item \textbf{MCQ:} What will \texttt{console.log(typeof [])} output?
    \textbf{Answer:} object (Arrays are objects in JS).

    \item \textbf{Code Analysis (Sessional 2 2024):}
    \begin{lstlisting}[language=JavaScript]
var arr1 = "web".split('');
var arr2 = arr1.reverse();
var arr3 = "Programming".split('');
arr2.push(arr3);
console.log("array 2: " + arr2);
    \end{lstlisting}
    \textbf{Explanation:} 
    1. \texttt{arr1} = ['w','e','b']. 
    2. \texttt{arr2} reference refers to \texttt{arr1} reversed: ['b','e','w']. Note: \texttt{reverse()} mutates in place if referencing same array, but here \texttt{split} creates new.
    3. \texttt{arr3} = ['P','r',...]. 
    4. \texttt{push} adds the \textit{entire array} \texttt{arr3} as a single element at the end.
    \newline \textbf{Output:} \texttt{b,e,w,P,r,o,g,r,a,m,m,i,n,g} (Browsers flatten for display string).

    \item \textbf{DOM Manipulation:} Write code to display user name N times.
    \begin{lstlisting}[language=JavaScript]
function displayName() {
  const num = document.getElementById('num').value;
  const list = document.getElementById('list');
  list.innerHTML = ''; // Clear previous
  for(let i=0; i<num; i++) {
     const li = document.createElement('li');
     li.textContent = "My Name";
     list.appendChild(li);
  }
}
    \end{lstlisting}
\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colback=gray!5,colframe=gray!75,title=Extra Practice Questions]
\subsubsection*{ES6 Features}
\begin{enumerate}[resume]
    \item Which keyword allows declaring a variable that cannot be reassigned?
    \textbf{Answer:} \texttt{const}

    \item Rewrite this using Arrow Functions:
    \begin{lstlisting}[language=JavaScript]
    function sum(a, b) { return a + b; }
    \end{lstlisting}
    \textbf{Answer:} \texttt{const sum = (a, b) => a + b;}
\end{enumerate}

\subsubsection*{Advanced Scoping}
\textbf{Question:} Output of the following?
\begin{lstlisting}[language=JavaScript]
console.log(a);
var a = 5;
\end{lstlisting}
\textbf{Answer:} \texttt{undefined}. (Reason: \texttt{var} declarations are hoisted, but initializations are not).
\end{tcolorbox}
