\subsection*{Comprehensive Exam Prep: React}

\begin{tcolorbox}[colback=orange!5,colframe=orange!75,title=Past Paper Questions (Sessional 2 2024 \& Final)]
\begin{enumerate}
    \item \textbf{Theory:} Difference between Real DOM and Virtual DOM?
    \begin{itemize}
        \item \textbf{Real DOM}: The actual HTML structure. Slow updates (heavy reflow/repaint).
        \item \textbf{Virtual DOM}: Lightweight JavaScript object copy. React updates this first, compares (diffing), and patches only changes to Real DOM (reconciliation).
    \end{itemize}

    \item \textbf{Theory:} List common React events.
    \newline \textbf{Answer:} \texttt{onClick}, \texttt{onChange}, \texttt{onSubmit}, \texttt{onMouseEnter}.

    \item \textbf{Theory:} What are Keys? Are they necessary?
    \newline \textbf{Answer:} Keys help React identify which items in a list have changed, added, or removed. They are necessary for performance and avoiding bugs in dynamic lists.

    \item \textbf{Task:} Create a Counter Component (Class-based).
\begin{lstlisting}[language=JavaScript]
class Counter extends React.Component {
  state = { count: 0 };
  increment = () => this.setState({ count: this.state.count + 1 });
  render() {
    return <button onClick={this.increment}>{this.state.count}</button>;
  }
}
\end{lstlisting}
\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colback=gray!5,colframe=gray!75,title=Extra Practice Questions]
\subsubsection*{Hooks & Functional Components}
\begin{enumerate}
    \item How do you replicate \texttt{componentDidMount} with \texttt{useEffect}?
    \newline \textbf{Answer:} \texttt{useEffect(() => \{ ... \}, [])} (Empty dependency array).

    \item \textbf{Code Snippet:} Create a component using \texttt{useState} to toggle text visibility.
\begin{lstlisting}[language=JavaScript]
function Toggle() {
  const [show, setShow] = useState(true);
  return (
    <div>
      <button onClick={() => setShow(!show)}>Toggle</button>
      {show && <p>Hidden Text</p>}
    </div>
  );
}
\end{lstlisting}
\end{enumerate}
\end{tcolorbox}
